\chapter{Basic Filtering}


This chapter introduces the most commonly used filters found in OTB.
Most of these filters are intended to process images. They will accept one or
more images as input and will produce one or more images as output. OTB is
based ITK's data pipeline architecture in which the output of one filter is
passed as input to another filter. (See Section
\ref{sec:DataProcessingPipeline} on page \pageref{sec:DataProcessingPipeline}
for more information.)


\section{Thresholding}
\ifitkFullVersion
\label{sec:ThresholdingFiltering}
\fi

The thresholding operation is used to change or identify pixel values based
on specifying one or more values (called the \emph{threshold} value). The
following sections describe how to perform thresholding operations using
OTB.

\subsection{Threshold to Point Set}
\label{sec:ThresholdImageToPointSetFilter}

\ifitkFullVersion
\input{ThresholdToPointSetExample.tex}
\fi



\section{Mathematical operations on images}
OTB and ITK provide a lot of filters allowing to perform basic operations on image layers (thresholding, ratio, layers combinations...).
It allows to create a processing chain defining at each step operations and to combine them in the data pipeline.
But the library offers also the possibility to perform more generic complex mathematical operation on images in a single filter: the
\doxygen{otb}{BandMathImageFilter} and more recently the \doxygen{otb}{BandMathImageFilterX}.

\subsection{BandMath filter}
\label{sec:BandMathImageFilter}

\ifitkFullVersion
\input{BandMathFilterExample.tex}
\fi

\subsection{BandMathX filter}
\label{sec:BandMathImageFilterX}
A new version of the BandMath filter is now available; among the new functionalities, variables representing multi-band pixels were introduced, as well as variables representing neighborhoods of pixels. The class name is \doxygen{otb}{BandMathImageFilterX}.

\ifitkFullVersion
\input{BandMathXImageFilterExample.tex}
\fi


\subsection{Ratio of Means Detector}
\input{TouziEdgeDetectorExample}


\subsubsection{Mean Shift filtering and clustering}
\label{sec:MeanShift}

\ifitkFullVersion
\input{MeanShiftSegmentationFilterExample.tex}
\fi



\subsection{Edge Preserving Speckle Reduction Filters}
\label{sec:SpeckleFilters}
\ifitkFullVersion
\input{LeeImageFilter.tex}
\input{FrostImageFilter.tex}
\fi



\subsection{Edge preserving Markov Random Field}

The Markov Random Field framework for OTB is more detailed in \ref{sec:MarkovRandomFieldOTB} (p. \pageref{sec:MarkovRandomFieldOTB}).

\index{Markov!Filtering}
\index{Markov!Restoration}
\ifitkFullVersion
\input{MarkovRestorationExample.tex}
\fi





