\chapter{System Overview}
\label{chapter:SystemOverview}

The purpose of this chapter is to provide you with an overview of the
\emph{ORFEO Toolbox} system. We recommend that you read this chapter to
gain an appreciation for the breadth and area of application of
OTB. In this chapter, we will make reference either to \emph{OTB
  features} or \emph{ITK features} without distinction. Bear in mind
that OTB uses ITK as its core element, so all the fundamental elements
of OTB come from ITK. OTB extends the functionalities of ITK for the
remote sensing image processing community. We benefit from the Open
Source development approach chosen for ITK, which allows us to provide
an impressive set of functionalities with much less effort than
would have been the case in a closed source universe!

\section{System Organization}
\label{sec:SystemOrganization}

The Orfeo Toolbox consists of several subsystems:

\begin{description}
	\item[Essential System Concepts.] Like any software system, OTB is
        built around some core design concepts. OTB uses those of
        ITK. Some of the more important
        concepts include generic programming, smart pointers for memory
        management, object factories for adaptable object instantiation,
        event management using the command/observer design paradigm, and
        multithreading support.

	\item[Numerics] OTB, as ITK uses VXL's VNL numerics libraries. These are
        easy-to-use C++ wrappers around the Netlib Fortran numerical 
        analysis routines (\url{http://www.netlib.org}).

	\item[Data Representation and Access.]  Two principal classes
        are used to represent data: the \doxygen{otb}{Image} and
        \doxygen{itk}{Mesh} classes.  In addition, various types of
        iterators and containers are used in ITK to hold and traverse
        the data. Other important but less popular classes are also
        used to represent data such as histograms.

	\item[ITK's Data Processing Pipeline.]  The data representation
	classes (known as \emph{data objects}) are operated on by
	\emph{filters} that in turn may be organized into data flow
	\emph{pipelines}. These pipelines maintain state and therefore
	execute only when necessary.  They also support
	multi-threading, and are streaming capable (i.e., can operate
	on pieces of data to minimize the memory footprint).

        \item[IO Framework.] Associated with the data processing
        pipeline are \emph{sources}, filters that initiate the
        pipeline, and \emph{mappers}, filters that terminate the
        pipeline.  The standard examples of sources and mappers are
        \emph{readers} and \emph{writers} respectively.  Readers
        input data (typically from a file), and writers output data
        from the pipeline. \emph{Viewers} are another example of mappers.

	\item[Spatial Objects.] Geometric shapes are represented in
        OTB using the ITK spatial object hierarchy.  These classes are
        intended to support modeling of anatomical structures in
        ITK. OTB uses them in order to model cartographic elements. Using a
        common basic interface, the spatial objects are capable of
        representing regions of space in a variety of different
        ways. For example: mesh structures, image masks, and implicit
        equations may be used as the underlying representation scheme.
        Spatial objects are a natural data structure for communicating
        the results of segmentation methods and for introducing
        geometrical priors in both segmentation and registration
        methods.

	\item[ITK's Registration Framework.] A flexible framework for
        registration supports four different types of registration:
        image registration, multiresolution registration, PDE-based
        registration, and FEM (finite element method) registration.

	\item[FEM Framework.] ITK includes a subsystem for solving general
        FEM problems, in particular non-rigid registration. The FEM package
        includes mesh definition (nodes and elements), loads, and boundary
        conditions.

	\item[Level Set Framework.] The level set framework is a set of
        classes for creating filters to solve partial differential equations
        on images using an iterative, finite difference update scheme. The
        level set framework consists of finite difference solvers including a
        sparse level set solver, a generic level set segmentation filter, and
        several specific subclasses including threshold, Canny, and Laplacian
        based methods.

	\item[Wrapping.] ITK uses a unique, powerful system for
	producing interfaces (i.e., ``wrappers'') to interpreted
	languages such as Tcl and Python. The GCC\_XML tool is used to
	produce an XML description of arbitrarily complex C++ code;
	CSWIG is then used to transform the XML description into
	wrappers using the \href{http://www.swig.org/}{SWIG}
	package. OTB does not use this system at present.

%% 	\item[Auxiliary / Utilities] Several auxiliary subsystems are 
%%         available to supplement other classes in the system. For example,
%%         calculators are classes that perform specialized operations in
%%         support of filters (e.g., MeanCalculator computes the mean of a
%%         sample). Other utilities include GDAL format file
%%         support, png, zlib, FLTK / Qt image viewers, and interfaces to the
%%         Visualization Toolkit (VTK) system.
        
\end{description}


\section{Essential System Concepts}
\label{sec:EssentialSystemConcepts}

This section describes some of the core concepts and implementation features
found in ITK and therefore also in OTB.

\subsection{Generic Programming}
\label{sec:GenericProgramming}

\index{generic programming}
\index{template}

Generic programming is a method of organizing libraries consisting of
generic---or reusable---software components. The idea is to
make software that is capable of ``plugging together'' in an efficient,
adaptable manner. The essential ideas of generic programming are
\emph{containers} to hold data, \emph{iterators} to access the data, and 
\emph{generic algorithms} that use containers and iterators to create 
efficient, fundamental algorithms such as sorting. Generic programming is
implemented in C++ with the \emph{template} programming mechanism and the 
use of the STL Standard Template Library.

C++ templating is a programming technique allowing users to write software in
terms of one or more unknown types \code{T}. To create executable code, the
user of the software must specify all types \code{T} (known as \emph{template
instantiation}) and successfully process the code with the compiler. The
\code{T} may be a native type such as
\code{float} or \code{int}, or \code{T} may be a user-defined type (e.g.,
\code{class}). At compile-time, the compiler makes sure that the templated 
types are compatible with the instantiated code and that the types are
supported by the necessary methods and operators.

ITK uses the techniques of generic programming in its implementation. The
advantage of this approach is that an almost unlimited variety of data types
are supported simply by defining the appropriate template types. For example,
in OTB it is possible to create images consisting of almost any type of
pixel. In addition, the type resolution is performed at compile-time, so the
compiler can optimize the code to deliver maximal performance. The
disadvantage of generic programming is that many compilers still do not
support these advanced concepts and cannot compile OTB. And even if they do,
they may produce completely undecipherable error messages due to even the
simplest syntax errors.

\subsection{Include Files and Class Definitions}
\label{sec:IncludeFiles}

In ITK and OTB classes are defined by a maximum of two files: a header \code{.h} file
and an implementation file---\code{.cxx} if a non-templated class, and a
\code{.hxx} if a templated class.
The header files contain class declarations
and formatted comments that are used by the Doxygen documentation
system to automatically produce HTML manual pages.

In addition to class headers, there are a few other important ITK header files.
\begin{description}
        \item[\code{itkMacro.h}] defines standard system-wide macros (such as \code{Set/Get},
        constants, and other parameters).

        \item[\code{itkNumericTraits.h}] defines numeric characteristics for native types such
        as its maximum and minimum possible values.

        \item[\code{itkWin32Header.h}] is used to define operating system parameters to control
        the compilation process.
\end{description}

\subsection{Object Factories}
\label{sec:ObjectFactories}

\index{object factory}
\index{factory}

Most classes in OTB are instantiated through an \emph{object factory}
mechanism. That is, rather than using the standard C++ class constructor and
destructor, instances of an OTB class are created with the static class
\code{New()} method. In fact, the constructor and destructor are
\code{protected:} so it is generally not possible to construct an OTB
instance on the heap. (Note: this behavior pertains to classes that are
derived from \doxygen{itk}{LightObject}. In some cases the need for speed or
reduced memory footprint dictates that a class not be derived from
LightObject and in this case instances may be created on the heap. An
example of such a class is \doxygen{itk}{EventObject}.)

The object factory enables users to control run-time instantiation of classes
by registering one or more factories with \doxygen{itk}{ObjectFactoryBase}. These
registered factories support the method \code{CreateInstance(classname)}
which takes as input the name of a class to create. The factory can choose to
create the class based on a number of factors including the computer system
configuration and environment variables. For example, in a particular
application an OTB user may wish to deploy their own class implemented using
specialized image processing hardware (i.e., to realize a performance
gain). By using the object factory mechanism, it is possible at run-time to
replace the creation of a particular OTB filter with such a custom class. (Of
course, the class must provide the exact same API as the one it is
replacing.) To do this, the user compiles their class (using the same compiler,
build options, etc.) and inserts the object code into a shared library or
DLL. The library is then placed in a directory referred to by the
\code{OTB\_AUTOLOAD\_PATH} environment variable. On instantiation, the object
factory will locate the library, determine that it can create a class of a
particular name with the factory, and use the factory to create the
instance. (Note: if the \code{CreateInstance()} method cannot find a factory
that can create the named class, then the instantiation of the class falls
back to the usual constructor.)

In practice object factories are used mainly (and generally transparently) by
the OTB input/output (IO) classes. For most users the greatest impact is on
the use of the \code{New()} method to create a class. Generally the
\code{New()} method is declared and implemented via the macro
\code{itkNewMacro()} found in \code{Modules/Core/Common/include/itkMacro.h}.


\subsection{Smart Pointers and Memory Management}
\label{sec:SmartPointers}

\index{smart pointer}

By their nature object-oriented systems represent and operate on data through
a variety of object types, or classes. When a particular class is
instantiated to produce an instance of that class, memory allocation occurs
so that the instance can store data attribute values and method pointers
(i.e., the vtable). This object may then be referenced by other classes or
data structures during normal operation of the program. Typically during
program execution all references to the instance may disappear at which point
the instance must be deleted to recover memory resources. Knowing when to
delete an instance, however, is difficult. Deleting the instance too soon
results in program crashes; deleting it too late and memory leaks (or
excessive memory consumption) will occur. This process of allocating and
releasing memory is known as memory management.

In ITK, memory management is implemented through reference counting. This
compares to another popular approach---garbage collection---used
\index{garbage collection} by many
systems including Java. In reference counting, a count of the number of
references to each instance is kept. When the reference goes to zero, the
object destroys itself. In garbage collection, a background process sweeps
the system identifying instances no longer referenced in the system and
deletes them. The problem with garbage collection is that the actual point in
time at which memory is deleted is variable. This is unacceptable when an
object size may be gigantic (think of a large 3D volume gigabytes in
size). Reference counting deletes memory immediately (once all references to
an object disappear).

Reference counting is implemented through a \code{Register()}/\code{Delete()}
member function interface.  All instances of an OTB object have a
\code{Register()} method invoked on them by any other object that references
an them. The \code{Register()} method increments the instances' reference
count. When the reference to the instance disappears, a \code{Delete()}
method is invoked on the instance that decrements the reference count---this
is equivalent to an \code{UnRegister()} method. When the reference count
returns to zero, the instance is destroyed.

This protocol is greatly simplified by using a helper class called a
\doxygen{itk}{SmartPointer}. The smart pointer acts like a regular pointer
(e.g. supports operators \code{->} and \code{*}) but automagically performs a
\code{Register()} when referring to an instance, and an \code{UnRegister()}
when it no longer points to the instance.  Unlike most other instances in
OTB, SmartPointers can be allocated on the program stack, and are
automatically deleted when the scope that the SmartPointer was created
is closed. As a result, you should \emph{rarely if ever call Register() or
Delete()} in OTB. For example:

\small
\begin{verbatim}
  MyRegistrationFunction()
    { <----- Start of scope

    // here an interpolator is created and associated to the
    // SmartPointer "interp".
    InterpolatorType::Pointer interp = InterpolatorType::New();

    } <------ End of scope
\end{verbatim}
\normalsize

In this example, reference counted objects are created (with the \code{New()}
method) with a reference count of one. Assignment to the SmartPointer
\code{interp} does not change the reference count. At the end of scope,
\code{interp} is destroyed, the reference count of the actual interpolator
object (referred to by \code{interp}) is decremented, and if it reaches zero,
then the interpolator is also destroyed.

Note that in ITK SmartPointers are always used to refer to instances of
classes derived from \doxygen{itk}{LightObject}. Method invocations and function
calls often return ``real'' pointers to instances, but they are immediately
assigned to a SmartPointer. Raw pointers are used for non-LightObject classes when
the need for speed and/or memory demands a smaller, faster class.


\section{Data Representation}
\label{sec:DataRepresentationAndAccess}

\index{data object} 

\index{otb::Image}

\doxygen{otb}{Image} represents an \emph{n}-dimensional, regular sampling of
data. The sampling direction is parallel to each of the coordinate axes, and
the origin of the sampling, inter-pixel spacing, and the number of samples in
each direction (i.e., image dimension) can be specified. The sample, or
pixel, type in OTB is arbitrary---a template parameter \code{TPixel}
specifies the type upon template instantiation. (The dimensionality of the
image must also be specified when the image class is instantiated.) The key
is that the pixel type must support certain operations (for example, addition
or difference) if the code is to compile in all cases (for example, to be
processed by a particular filter that uses these operations). In practice the
OTB user will use a C++ simple type (e.g., \code{int}, \code{float}) or a pre-defined pixel
type and will rarely create a new type of pixel class.

One of the important ITK concepts regarding images is that rectangular,
continuous pieces of the image are known as \emph{regions}. Regions are used
to specify which part of an image to process, for example in multithreading,
or which part to hold in memory. In ITK there are three common types of
regions:
\begin{enumerate}
\item \code{LargestPossibleRegion}---the image in its entirety.
\item \code{BufferedRegion}---the portion of the image retained in memory.
\item \code{RequestedRegion}---the portion of the region requested by a 
filter or other class when operating on the image.
\end{enumerate}

The \doxygen{otb}{Image} class extends the functionalities of the
\doxygen{itk}{Image} in order to take into account particular remote
sensing features as geographical projections, etc.

\section{Data Processing Pipeline}
\label{sec:DataProcessingPipeline}

\index{data processing pipeline}

\index{process object} 
\index{source}
\index{reader} 
\index{filter} 
\index{mapper} 

While data objects (e.g., images) are used to represent data,
\emph{process objects} are classes that operate on data objects and may
produce new data objects. Process objects are classed as
\emph{sources}, \emph{filter objects}, or \emph{mappers}.  Sources (such as
readers) produce data, filter objects take in data and process it to produce
new data, and mappers accept data for output either to a file or
some other system.  Sometimes the term \emph{filter} is used broadly
to refer to all three types.

\index{streaming}

The data processing pipeline ties together data objects (e.g., images)
and process objects. The pipeline supports an automatic updating
mechanism that causes a filter to execute if and only if its input 
or its internal state changes. Further, the data pipeline supports
\emph{streaming}, the ability to automatically break data into smaller
pieces, process the pieces one by one, and reassemble the processed data into
a final result.

Typically data objects and process objects are connected together using the
\code{SetInput()} and \code{GetOutput()} methods as follows:

\small
\begin{verbatim}
  typedef otb::Image<float,2> FloatImage2DType;

  itk::RandomImageSource<FloatImage2DType>::Pointer random;
  random = itk::RandomImageSource<FloatImage2DType>::New();
  random->SetMin(0.0);
  random->SetMax(1.0);

  itk::ShrinkImageFilter<FloatImage2DType,FloatImage2DType>::Pointer shrink;
  shrink = itk::ShrinkImageFilter<FloatImage2DType,FloatImage2DType>::New();
  shrink->SetInput(random->GetOutput());
  shrink->SetShrinkFactors(2);

  otb::ImageFileWriter::Pointer<FloatImage2DType> writer;
  writer = otb::ImageFileWriter::Pointer<FloatImage2DType>::New();
  writer->SetInput (shrink->GetOutput());
  writer->SetFileName( ``test.raw'' );
  writer->Update();
\end{verbatim}
\normalsize 

In this example the source object \doxygen{itk}{RandomImageSource} is connected
to the \doxygen{itk}{ShrinkImageFilter}, and the shrink filter is connected to
the mapper \doxygen{otb}{ImageFileWriter}. When the \code{Update()} method is
invoked on the writer, the data processing pipeline causes each of these
filters in order, culminating in writing the final data to a file on disk.
