\chapter{How to write an application}
\label{sec:writeAnApplication}

This chapter presents the different steps to write your own application.
It also contains a description of the framework surrounding the applications.

\section{Application design}
\label{sec:appDesign}
The first logical step is to define the role of your application:
\begin{itemize}
  \item What is the function of your application ? Try to draw a box diagram to 
  describe the design of your application. Note that you don't have to worry 
  about opening and saving image (or vector data) files, this is handled by the 
  framework.
  \item What variables (or data objects) must be exposed outside the application ?
  Try to make a list of the inputs, outputs and parameters of your application.
\end{itemize}
Then you should have a good vision of your application pipeline. Depending on the 
different filters used, the application can be streamed and threaded. The threading
capabilities can be different between the filters so there is no overall threading 
parameter (by default, each filter has its own threading settings). 

It is a different story for streaming. Since the image writers are handled within 
the framework and outside the reach of the developer, the default behaviour is to 
use streaming. If one of the filters doesn't support streaming, it will enlarge 
the requested output region to the largest possible region and the entire image 
will be processed at once. As a result, the developer doesn't have to handle  
streaming nor threading. However, there is a way to choose the number of streaming 
divisions (see section \ref{sec:appParam}).

\section{Architecture of the class}
\label{sec:appArchitecture}
Every application derive from the class \subdoxygen{otb}{Wrapper}{Application}. An 
application can't be templated. It must contain the standard class typedefs and
a call to the \code{OTB\_APPLICATION\_EXPORT} macro.

You need also to define standard macros \doxygen{itk}{NewMacro} and
\doxygen{itk}{TypeMacro}.
 
It is also mandatory to implement three methods in a new application:
\begin{itemize}
  \item \code{DoInit()}
  \item \code{DoUpdateParameters()}
  \item \code{DoExecute()}
\end{itemize}

\subsection{DoInit()}
\label{sec:appDoInit}
This method is called once, when the application is instantiated. It should 
contain the following actions:
\begin{itemize}
  \item Set the name and the description of the application
  \item Fill the documentation and give an example
  \item Declare all the parameters
  \item Define the documentation link:
    \item for contrib application use SetDocLink("\textit{docLink}") function defined in \subdoxygen{otb}{Wrapper}{Application}
    \item for official application use SetOfficialDocLink() function defined in \subdoxygen{otb}{Wrapper}{Application}
\end{itemize}


\subsection{DoUpdateParameters()}
\label{sec:appDoUpdateParameters}
This method is called after every modification of a parameter value. With the command 
line launcher, it is called each time a parameter is loaded. With the Qt launcher, it
is called each time a parameter field is modified. It can be used to maintain consistency and relationship
between parameters (e.g. in ExtractROI: when changing the input image, maybe the ROI size 
has to be updated).

\subsection{DoExecute()}
\label{sec:appDoExecute}
This method contains the real action of the application. This is where the pipeline 
must be set up. The application framework provides different methods to get a value 
or an object associated to a parameter:
\begin{itemize}
  \item \code{GetParameterInt(key)} : get the integer value of a parameter
  \item \code{GetParameterFloat(key)} : get the float value of a parameter
  \item \code{GetParameterString(key)} : get the string value of a parameter
  \item \code{GetParameterImage(key)} : get a pointer to an image object, read from the
  file name given in input
  \item \dots
\end{itemize}

where \code{key} refers to parameter key, defined using \code{AddParameter()} method in \code{DoInit()} method.

Similar methods exist for binding a data object to an output parameter:
\begin{itemize}
  \item \code{SetParameterOutputImage(key,data)} : link the image object to the given output parameter
  \item \code{SetParameterComplexOutputImage(key,data)} : link the complex image object to the given output parameter
  \item \code{SetParameterOutputVectorData(key,data)} : link the vector data object to the given
  output parameter
\end{itemize}

If possible, no filter update should be called inside this function. The update will be 
automatically called afterwards : for every image or vector data output, a writer is 
created and updated.

\subsection{Parameters selection}
\label{sec:appParam}
In the new application framework, every input, output or parameter derive from 
\subdoxygen{otb}{Wrapper}{Parameter}. The application engine supplies the following 
types of parameters:
\begin{itemize}
  \item \code{ParameterType\_Bool} : parameter storing a boolean. 
  \item \code{ParameterType\_Int} : parameter storing an integer.
  \item \code{ParameterType\_Radius} : parameter storing a radius.
  \item \code{ParameterType\_Float} : parameter storing a float.
  \item \code{ParameterType\_String} : parameter storing character string.
  \item \code{ParameterType\_StringList} : parameter storing a list of character string.
  \item \code{ParameterType\_InputFilename} : parameter storing an input file name.
  \item \code{ParameterType\_InputFilenameList} : parameter storing a list of input file names.
  \item \code{ParameterType\_Directory} : parameter storing a folder name.
  \item \code{ParameterType\_Group} : parameter storing children parameters.
  \item \code{ParameterType\_Choice} : parameter storing a list of choices (doesn't support
  multi-choice). It also allows to create specific sub-parameters for each available choice.
  \item \code{ParameterType\_ListView} : parameter storing a list of choices (support 
  multi-choice and single-choice).
  \item \code{ParameterType\_InputImage} : parameter storing an input image.
  \item \code{ParameterType\_InputImageList} : parameter storing a list of input image.
  \item \code{ParameterType\_ComplexInputImage} : parameter storing a complex input image.
  \item \code{ParameterType\_InputVectorData} : parameter storing input vector data.
  \item \code{ParameterType\_InputVectorDataList} : parameter storing a list of input vector data.
  \item \code{ParameterType\_InputProcessXML} : parameter storing an input XML file name.
  \item \code{ParameterType\_OutputFilename} : parameter storing an output file name.
  \item \code{ParameterType\_OutputImage} : parameter storing an output image.
  \item \code{ParameterType\_ComplexOutputImage} : parameter storing a complex output image.
  \item \code{ParameterType\_OutputVectorData} : parameter storing an output vector data.
  \item \code{ParameterType\_OutputProcessXML} : parameter storing an output XML file name.
  \item \code{ParameterType\_RAM} : parameter storing the maximum amount of RAM to be used.
\end{itemize}
\textbf{Note :} The former \code{ParameterType\_Empty} is \textbf{deprecated} and shall be replaced by \code{ParameterType\_Bool}.

\subsection{Parameters description}

Each created parameter has a unique key and several boolean flags to represent its state. These flags
can be used to set a parameter optional or test if the user has modified the parameter value. The parameters
are created in the \code{DoInit()} method, then the framework will set their value (either by parsing the 
command line or reading the graphical user interface). The \code{DoExecute()} method is called when all 
mandatory parameters have been given a value, which can be obtained with "Get" methods defined in 
\subdoxygen{otb}{Wrapper}{Application}. Parameters are set mandatory (or not) using \code{MandatoryOn(key)} method (\code{MandatoryOff(key)}).

Some functions are specific to numeric parameters, such as \code{SetMinimumParameterIntValue(key,value)}
or \code{SetMaximumParameterFloatValue(key,value)}. By default, numeric parameters are treated as inputs.
If your application outputs a number, you can use a numeric parameter and change its role by calling 
\code{SetParameterRole(key,Role\_Output)}.

The input types \code{InputImage}, \code{InputImageList}, \code{ComplexInputImage}, \code{InputVectorData}
and \code{InputVectorDataList} store the name of the files to load, but they also encapsulate the 
readers needed to produce the input data.

The output types \code{OutputImage}, \code{ComplexOutputImage} and \code{OutputVectorData} store the 
name of the files to write, but they also encapsulate the corresponding writers.

\section{Composite application}

The application framework has been extended to allow the implementation of composite applications :
\textbf{applications that use other applications}. The concept is simple : you have two applications A and B
that you want to chain in order to build a third application C. Rather than writing C by copying
the code of A and B, you would like to re-use applications A and B. This plain example will be
re-used in this section for explanations.

A dedicated class \subdoxygen{otb}{Wrapper}{CompositeApplication} has been added to create such applications.
If you derive this class to implement application C, you will be able to create a composite application.

\subsection{Creating internal applications}

Like with standard applications, you have to write a \code{DoInit()} function. In this function,
you should first clean any internal application with the function \code{ClearApplications()}
(the \code{DoInit()} function is called twice in some cases). Then you can
instantiate the internal applications that you want to use (for instance A and B).
The function \code{AddApplication()} will do that, based on :
\begin{itemize}
\item The application type (i.e. its official name, such as ExtractROI, BandMath, \dots)
\item An identifier : like with parameter keys, you have to specify an identifier
to refer to this internal application. Use the same naming conventions as parameters.
\item A description : give a small description of the role of this internal application.
\end{itemize}

Using the function \code{GetInternalApplication()}, you can get a pointer to the
internal application corresponding to a given identifier.

In the example given in introduction, we assume that :
\begin{itemize}
\item An internal application of type A has been added with identifier \code{a}
\item An internal application of type B has been added with identifier \code{b}
\end{itemize}

\subsection{Connecting parameters}

Once you have internal applications, you may want to setup their parameters. There
are typically 3 cases.

You may want to expose a parameter of an internal application as a parameter of
your composite application. Let say you want to expose parameter \code{io.in} from application
\code{a} into your composite application C with the key \code{input}. You can call the function :

\code{ShareParameter("input","a.io.in")}

As a result, the parameters \code{input} in application C and \code{io.in} in application \code{a}
will point to the same object. Under the two parameter keys, there is a unique value.
These two parameters can be considered as synchronized.

This leads to the second case : you may want to synchronize two parameters from internal
applications. Let say you want to synchronize parameter \code{field} from application
\code{a} with parameter \code{fname} from application \code{b}. You can call the function :

\code{Connect("a.field","b.fname")}

Note that the functions \code{ShareParameter()} and \code{Connect()} :
\begin{itemize}
\item Use the same syntax to access internal parameters ("application identifier"
dot "parameter key").
\item Shall be used in the DoInit() function, after the internal applications
have been added.
\end{itemize}

In this synchronization, the two parameters should have the same type, or have a
similar interface, such as input and output filenames that are both accessed using
\code{GetParameterString()} and \code{SetParameterString()}.

This type of connection is a transition to the third case : you may want to connect
the output of an internal application to the input of an other internal application.
Here the difficulty is that the two parameters to connect probably have different
types. Let say you want to connect parameter \code{a.out} to parameter \code{b.in}.
The "Connect()" function may work in favorable cases (see previous paragraph),
but for images, you have two options :
\begin{itemize}
\item Explicitly copy the image pointer from the output image parameter in the input
image parameter (with functions \code{SetParameterInputImage()} and
\code{GetParameterOutputImage()}). It will connect the pipelines in applications
A and B, to form an "in-memory" connexion. This has to be done between the calls
to \code{DoExecute()} of application A and B.
\item Use a temporary filename to store the output image \code{a.out} and read it
with \code{b.in}. In this case, you have to manually call the writers of parameter
\code{a.out}.
\end{itemize}

At the moment, the in-memory connexion of vector data parameters is not supported.

\subsection{Orchestration}

In the \code{DoExecute()} of your composite application, you have to call \code{ExecuteInternal()}
in order to launch each internal application. The order should be compatible with
image parameter connexions. If you want to do "in-memory" connexions, you can do it between
two calls to \code{ExecuteInternal()}, for instance :

\begin{cppcode}
ExecuteInternal("a");
GetInternalApplication("b")->SetParameterInputImage("in",
  GetInternalApplication("a")->GetParameterOutputImage("out"));
ExecuteInternal("b");
\end{cppcode}

The application BundleToPerfectSensor is a simple example of composite applications.
For a more complex example, you can check the application TrainImagesClassifier.

\section{Compile your application}

In order to compile your application you must call the macro \code{OTB\_CREATE\_APPLICATION} in the \emph{CMakelists.txt} file. 
This macro generates the lib \emph{otbapp\_XXX.so}, in (OTB\_BINARY\_DIR/lib/otb/applications), where \emph{XXX} refers to the class name.

\section{Execute your application}

There are different ways to launch applicatons :

\begin{description}
\item[CommandLine :] The command line option is invoked using \emph{otbApplicationLauncherCommandLine} executable followed by the classname, the application dir and the application parameters.
\item[QT :] Application can be encapsuled in Qt framework using \emph{otbApplicationLauncherQt} executable followed by the classname and the application dir.
\item[Python :] A Python wrapper is also available.
\end{description}


\section{Testing your application}
\label{sec:appTesting}
It is possible to write application tests. They are quite similar to filters tests.
The macro \code{OTB\_TEST\_APPLICATION} makes it easy to define a new test.


\section{Application Example}
\label{sec:ApplicationExample}
\ifitkFullVersion
\input{ApplicationExample.tex}
\fi

