\chapter{System Overview}
\label{chapter:SystemOverview}

The purpose of this chapter is to provide you with an overview of the
\emph{ORFEO Toolbox} system. We recommend that you read this chapter to
gain an appreciation for the breadth and area of application of
OTB. In this chapter, we will make reference either to \emph{OTB
  features} or \emph{ITK features} without distinction. Bear in mind
that OTB uses ITK as its core element, so all the fundamental elements
of OTB come from ITK. OTB extends the functionalities of ITK for the
remote sensing image processing comunity. We benefit from the Open
Source development approach chosen for ITK, which allows us to provide
an impressive set of functionalities with much lesser effort than it
would have been the case in a closed source universe!

\section{System Organization}
\label{sec:SystemOrganization}

The ORFEO Toolbox consists of several subsystems. A brief
description of these subsystems follows. Later sections in this chapter---and
in some cases additional chapters---cover these concepts in more detail. (Note:
in the previous chapter two other modules---\code{OTB-Documents} and
\code{OTB-Applications} were briefly described.)

\begin{description}
	\item[Essential System Concepts.] Like any software system, OTB is
        built around some core design concepts. OTB uses those of
        ITK. Some of the more important
        concepts include generic programming, smart pointers for memory
        management, object factories for adaptable object instantiation,
        event management using the command/observer design paradigm, and
        multithreading support.

	\item[Numerics] OTB, as ITK uses VXL's VNL numerics libraries. These are
        easy-to-use C++ wrappers around the Netlib Fortran numerical 
        analysis routines (\url{http://www.netlib.org}).

	\item[Data Representation and Access.]  Two principal classes
        are used to represent data: the \doxygen{otb}{Image} and
        \doxygen{itk}{Mesh} classes.  In addition, various types of
        iterators and containers are used in ITK to hold and traverse
        the data. Other important but less popular classes are also
        used to represent data such as histograms.

	\item[ITK's Data Processing Pipeline.]  The data representation
	classes (known as \emph{data objects}) are operated on by
	\emph{filters} that in turn may be organized into data flow
	\emph{pipelines}. These pipelines maintain state and therefore
	execute only when necessary.  They also support
	multi-threading, and are streaming capable (i.e., can operate
	on pieces of data to minimize the memory footprint).

        \item[IO Framework.] Associated with the data processing
        pipeline are \emph{sources}, filters that initiate the
        pipeline, and \emph{mappers}, filters that terminate the
        pipeline.  The standard examples of sources and mappers are
        \emph{readers} and \emph{writers} respectively.  Readers
        input data (typically from a file), and writers output data
        from the pipeline. \emph{Viewers} are another example of mappers.

	\item[Spatial Objects.] Geometric shapes are represented in
        OTB using the ITK spatial object hierarchy.  These classes are
        intended to support modeling of anatomical structures in
        ITK. OTB uses them in order to model cartographic elements. Using a
        common basic interface, the spatial objects are capable of
        representing regions of space in a variety of different
        ways. For example: mesh structures, image masks, and implicit
        equations may be used as the underlying representation scheme.
        Spatial objects are a natural data structure for communicating
        the results of segmentation methods and for introducing
        geometrical priors in both segmentation and registration
        methods.

	\item[ITK's Registration Framework.] A flexible framework for
        registration supports four different types of registration:
        image registration, multiresolution registration, PDE-based
        registration, and FEM (finite element method) registration.

	\item[FEM Framework.] ITK includes a subsystem for solving general
        FEM problems, in particular non-rigid registration. The FEM package
        includes mesh definition (nodes and elements), loads, and boundary
        conditions.

	\item[Level Set Framework.] The level set framework is a set of
        classes for creating filters to solve partial differential equations
        on images using an iterative, finite difference update scheme. The
        level set framework consists of finite difference solvers including a
        sparse level set solver, a generic level set segmentation filter, and
        several specific subclasses including threshold, Canny, and Laplacian
        based methods.

	\item[Wrapping.] ITK uses a unique, powerful system for
	producing interfaces (i.e., ``wrappers'') to interpreted
	languages such as Tcl and Python. The GCC\_XML tool is used to
	produce an XML description of arbitrarily complex C++ code;
	CSWIG is then used to transform the XML description into
	wrappers using the \href{http://www.swig.org/}{SWIG}
	package. OTB does not use this system at present.

	\item[Auxiliary / Utilities] Several auxiliary subsystems are 
        available to supplement other classes in the system. For example,
        calculators are classes that perform specialized operations in
        support of filters (e.g., MeanCalculator computes the mean of a
        sample). Other utilities include GDAL format file
        support, png, zlib, FLTK / Qt image viewers, and interfaces to the
        Visualization Toolkit (VTK) system.
        
\end{description}


\section{Essential System Concepts}
\label{sec:EssentialSystemConcepts}

This section describes some of the core concepts and implementation features
found in ITK and therefore also in OTB.

\subsection{Generic Programming}
\label{sec:GenericProgramming}

\index{generic programming}
\index{template}

Generic programming is a method of organizing libraries consisting of
generic---or reusable---software components \cite{Musser1996}. The idea is to
make software that is capable of ``plugging together'' in an efficient,
adaptable manner. The essential ideas of generic programming are
\emph{containers} to hold data, \emph{iterators} to access the data, and 
\emph{generic algorithms} that use containers and iterators to create 
efficient, fundamental algorithms such as sorting. Generic programming is
implemented in C++ with the \emph{template} programming mechanism and the 
use of the STL Standard Template Library \cite{Austern1999}.

C++ templating is a programming technique allowing users to write software in
terms of one or more unknown types \code{T}. To create executable code, the
user of the software must specify all types \code{T} (known as \emph{template
instantiation}) and successfully process the code with the compiler. The
\code{T} may be a native type such as
\code{float} or \code{int}, or \code{T} may be a user-defined type (e.g.,
\code{class}). At compile-time, the compiler makes sure that the templated 
types are compatible with the instantiated code and that the types are
supported by the necessary methods and operators.

ITK uses the techniques of generic programming in its implementation. The
advantage of this approach is that an almost unlimited variety of data types
are supported simply by defining the appropriate template types. For example,
in OTB it is possible to create images consisting of almost any type of
pixel. In addition, the type resolution is performed at compile-time, so the
compiler can optimize the code to deliver maximal performance. The
disadvantage of generic programming is that many compilers still do not
support these advanced concepts and cannot compile OTB. And even if they do,
they may produce completely undecipherable error messages due to even the
simplest syntax errors. If you are not familiar with templated code and
generic programming, we recommend the two books cited above.

\subsection{Include Files and Class Definitions}
\label{sec:IncludeFiles}

In ITK and OTB classes are defined by a maximum of two files: a header \code{.h} file
and an implementation file---\code{.cxx} if a non-templated class, and a
\code{.txx} if a templated class.
The header files contain class declarations
and formatted comments that are used by the Doxygen documentation
system to automatically produce HTML manual pages.

In addition to class headers, there are a few other important header files.
\begin{description}
        \item[\code{itkMacro.h}] is found in the
        \code{Utilities/ITK/Code/Common} directory
        and defines standard system-wide macros (such as \code{Set/Get},
        constants, and other parameters).

        \item[\code{itkNumericTraits.h}] is found in the \code{Utilities/ITK/Code/Common}
        directory and defines numeric characteristics for native types such
        as its maximum and minimum possible values.

        \item[\code{itkWin32Header.h}] is found in the \code{Utilities/ITK/Code/Common}
        and is used to define operating system parameters to control
        the compilation process.
\end{description}

\subsection{Object Factories}
\label{sec:ObjectFactories}

\index{object factory}
\index{factory}

Most classes in OTB are instantiated through an \emph{object factory}
mechanism. That is, rather than using the standard C++ class constructor and
destructor, instances of an OTB class are created with the static class
\code{New()} method. In fact, the constructor and destructor are
\code{protected:} so it is generally not possible to construct an OTB
instance on the heap. (Note: this behavior pertains to classes that are
derived from \doxygen{itk}{LightObject}. In some cases the need for speed or
reduced memory footprint dictates that a class not be derived from
LightObject and in this case instances may be created on the heap. An
example of such a class is \doxygen{itk}{EventObject}.)

The object factory enables users to control run-time instantiation of classes
by registering one or more factories with \doxygen{itk}{ObjectFactoryBase}. These
registered factories support the method \code{CreateInstance(classname)}
which takes as input the name of a class to create. The factory can choose to
create the class based on a number of factors including the computer system
configuration and environment variables. For example, in a particular
application an OTB user may wish to deploy their own class implemented using
specialized image processing hardware (i.e., to realize a performance
gain). By using the object factory mechanism, it is possible at run-time to
replace the creation of a particular OTB filter with such a custom class. (Of
course, the class must provide the exact same API as the one it is
replacing.) To do this, the user compiles her class (using the same compiler,
build options, etc.) and inserts the object code into a shared library or
DLL. The library is then placed in a directory referred to by the
\code{OTB\_AUTOLOAD\_PATH} environment variable. On instantiation, the object
factory will locate the library, determine that it can create a class of a
particular name with the factory, and use the factory to create the
instance. (Note: if the \code{CreateInstance()} method cannot find a factory
that can create the named class, then the instantiation of the class falls
back to the usual constructor.)

In practice object factories are used mainly (and generally transparently) by
the OTB input/output (IO) classes. For most users the greatest impact is on
the use of the \code{New()} method to create a class. Generally the
\code{New()} method is declared and implemented via the macro
\code{itkNewMacro()} found in \code{Utilities/ITK/Common/itkMacro.h}.


\subsection{Smart Pointers and Memory Management}
\label{sec:SmartPointers}

\index{smart pointer}

By their nature object-oriented systems represent and operate on data through
a variety of object types, or classes. When a particular class is
instantiated to produce an instance of that class, memory allocation occurs
so that the instance can store data attribute values and method pointers
(i.e., the vtable). This object may then be referenced by other classes or
data structures during normal operation of the program. Typically during
program execution all references to the instance may disappear at which point
the instance must be deleted to recover memory resources. Knowing when to
delete an instance, however, is difficult. Deleting the instance too soon
results in program crashes; deleting it too late and memory leaks (or
excessive memory consumption) will occur. This process of allocating and
releasing memory is known as memory management.

In ITK, memory management is implemented through reference counting. This
compares to another popular approach---garbage collection---used
\index{garbage collection} by many
systems including Java. In reference counting, a count of the number of
references to each instance is kept. When the reference goes to zero, the
object destroys itself. In garbage collection, a background process sweeps
the system identifying instances no longer referenced in the system and
deletes them. The problem with garbage collection is that the actual point in
time at which memory is deleted is variable. This is unacceptable when an
object size may be gigantic (think of a large 3D volume gigabytes in
size). Reference counting deletes memory immediately (once all references to
an object disappear).

Reference counting is implemented through a \code{Register()}/\code{Delete()}
member function interface.  All instances of an OTB object have a
\code{Register()} method invoked on them by any other object that references
an them. The \code{Register()} method increments the instances' reference
count. When the reference to the instance disappears, a \code{Delete()}
method is invoked on the instance that decrements the reference count---this
is equivalent to an \code{UnRegister()} method. When the reference count
returns to zero, the instance is destroyed.

This protocol is greatly simplified by using a helper class called a
\doxygen{itk}{SmartPointer}. The smart pointer acts like a regular pointer
(e.g. supports operators \code{->} and \code{*}) but automagically performs a
\code{Register()} when referring to an instance, and an \code{UnRegister()}
when it no longer points to the instance.  Unlike most other instances in
OTB, SmartPointers can be allocated on the program stack, and are
automatically deleted when the scope that the SmartPointer was created
is closed. As a result, you should \emph{rarely if ever call Register() or
Delete()} in OTB. For example:

\small
\begin{verbatim}
  MyRegistrationFunction()
    { <----- Start of scope

    // here an interpolator is created and associated to the
    // SmartPointer "interp".
    InterpolatorType::Pointer interp = InterpolatorType::New();

    } <------ End of scope
\end{verbatim}
\normalsize

In this example, reference counted objects are created (with the \code{New()}
method) with a reference count of one. Assignment to the SmartPointer
\code{interp} does not change the reference count. At the end of scope,
\code{interp} is destroyed, the reference count of the actual interpolator
object (referred to by \code{interp}) is decremented, and if it reaches zero,
then the interpolator is also destroyed.

Note that in ITK SmartPointers are always used to refer to instances of
classes derived from \doxygen{itk}{LightObject}. Method invocations and function
calls often return ``real'' pointers to instances, but they are immediately
assigned to a SmartPointer. Raw pointers are used for non-LightObject classes when
the need for speed and/or memory demands a smaller, faster class.


\subsection{Error Handling and Exceptions}
\label{sec:ErrorHandling}

\index{exceptions}
\index{error handling}

In general, OTB uses exception handling to manage errors during program
execution. Exception handling is a standard part of the C++ language and
generally takes the form as illustrated below:
\small
\begin{verbatim}
  try
    {
    //...try executing some code here...
    }
  catch ( itk::ExceptionObject exp )
    {
    //...if an exception is thrown catch it here
    }
\end{verbatim}
\normalsize

where a particular class may throw an exceptions as demonstrated below (this
code snippet is taken from \doxygen{itk}{ByteSwapper}:
\small
\begin{verbatim}
  switch ( sizeof(T) )
    {
    //non-error cases go here followed by error case  
    default:  
      ByteSwapperError e(__FILE__, __LINE__);
      e.SetLocation("SwapBE");
      e.SetDescription("Cannot swap number of bytes requested");
      throw e;
    }
\end{verbatim}
\normalsize

Note that \doxygen{itk}{ByteSwapperError} is a subclass of
\doxygen{itk}{ExceptionObject}. (In fact in OTB all exceptions should be derived
from \code{itk::ExceptionObject}.) In this example a special constructor and C++
preprocessor variables \code{\_\_FILE\_\_} and \code{\_\_LINE\_\_} are used to instantiate
the exception object and provide additional information to the user. You can
choose to catch a particular exception and hence a specific OTB error, or you
can trap \emph{any} OTB exception by catching ExceptionObject.


\subsection{Event Handling}
\label{sec:EventHandling}

\index{event handling}
\index{Command/Observer design pattern}
\index{itk::Command}
\index{ProgressEvent()}
\index{InvokeEvent()}

Event handling in OTB is implemented using the Subject/Observer design
pattern \cite{Gamma1995} (sometimes referred to as the Command/Observer
design pattern). In this approach, objects indicate that they are watching
for a particular event---invoked by a particular instance--by registering
with the instance that they are watching.  For example, filters in OTB
periodically invoke the \doxygen{itk}{ProgressEvent}. Objects that have registered
their interest in this event are notified when the event occurs. The
notification occurs via an invocation of a command (i.e., function callback,
method invocation, etc.) that is specified during the registration
process. (Note that events in OTB are subclasses of EventObject; look
in \code{itkEventObject.h} to determine which events are available.)

To recap via example: various objects in OTB will invoke specific events
as they execute (from ProcessObject):
\small
\begin{verbatim}
  this->InvokeEvent( ProgressEvent() );
\end{verbatim}
\normalsize

To watch for such an event, registration is required that associates a
command (e.g., callback function) with the event:
\code{Object::AddObserver()} method:
\small
\begin{verbatim}
  unsigned long progressTag = 
    filter->AddObserver(ProgressEvent(), itk::Command*);
\end{verbatim}
\normalsize

When the event occurs, all registered observers are notified via invocation
of the associated \code{Command::Execute()} method. Note that several
subclasses of Command are available supporting const and
non-const member functions as well as C-style functions. (Look in
\code{Common/Command.h} to find pre-defined subclasses of
Command. If nothing suitable is found, derivation is another
possibility.)

\subsection{Multi-Threading}
\label{sec:MultiThreading}

Multithreading is handled in OTB through ITK's high-level design
abstraction. This approach provides portable multithreading and hides the
complexity of differing thread implementations on the many systems supported
by OTB. For example, the class \doxygen{itk}{MultiThreader} provides support for
multithreaded execution using \code{sproc()} on an SGI, or
\code{pthread\_create} on any platform supporting POSIX threads. 

Multithreading is typically employed by an algorithm during its execution
phase. MultiThreader can be used to execute a single method on
multiple threads, or to specify a method per thread. For example, in the 
class \doxygen{itk}{ImageSource} (a superclass for most image processing filters)
the \code{GenerateData()} method uses the following methods:

\small
\begin{verbatim}
  multiThreader->SetNumberOfThreads(int);
  multiThreader->SetSingleMethod(ThreadFunctionType, void* data);
  multiThreader->SingleMethodExecute();
\end{verbatim}
\normalsize

In this example each thread invokes the same method. The multithreaded filter
takes care to divide the image into different regions that do not overlap for
write operations.

The general philosophy in ITK regarding thread safety is that accessing
different instances of a class (and its methods) is a thread-safe operation.
Invoking methods on the same instance in different threads is to be avoided.


\section{Numerics}
\label{sec:Numerics}

\index{VNL}
\index{numerics}

OTB; as ITK, uses the VNL numerics library to provide resources for numerical
programming combining the ease of use of packages like Mathematica and Matlab
with the speed of C and the elegance of C++. It provides a C++ interface to
the high-quality Fortran routines made available in the public domain by
numerical analysis researchers. ITK extends the functionality of VNL
by including interface classes between VNL and ITK proper.

The VNL numerics library includes classes for
\begin{description}
        \item[Matrices and vectors.] Standard matrix and vector support
        and operations on these types.

        \item[Specialized matrix and vector classes.] Several special matrix
        and vector class with special numerical properties are
        available. Class \code{vnl\_diagonal\_matrix} provides a fast and
        convenient diagonal matrix, while fixed size matrices and vectors
        allow "fast-as-C" computations (see \code{vnl\_matrix\_fixed<T,n,m>} 
        and example subclasses \code{vnl\_double\_3x3} and 
        \code{vnl\_double\_3}).

        \item[Matrix decompositions.] Classes \code{vnl\_svd<T>}, 
        \code{vnl\_symmetric\_eigensystem<T>}, and 
        \code{vnl\_generalized\_eigensystem}. 

        \item[Real polynomials.] Class \code{vnl\_real\_polynomial} stores 
        the coefficients of a real polynomial, and provides methods of 
        evaluation of the polynomial at any x, while class 
        \code{vnl\_rpoly\_roots} provides a root finder. 

        \item[Optimization.] Classes \code{vnl\_levenberg\_marquardt},
        \code{vnl\_amoeba}, \code{vnl\_conjugate\_gradient}, 
        \code{vnl\_lbfgs} allow optimization of user-supplied
        functions either with or without user-supplied derivatives.

        \item[Standardized functions and constants.] Class \code{vnl\_math}
        defines constants (pi, e, eps...) and simple functions (sqr, abs,
        rnd...). Class \code{numeric\_limits} is from the ISO standard
        document, and provides a way to access basic limits of a
        type. For example \code{numeric\_limits<short>::max()} returns the maximum
        value of a short.
\end{description}

Most VNL routines are implemented as wrappers around the high-quality Fortran
routines that have been developed by the numerical analysis community over
the last forty years and placed in the public domain. The central repository
for these programs is the "netlib" server \url{http://www.netlib.org/}. The
National Institute of Standards and Technology (NIST) provides an excellent
search interface to this repository in its \emph{Guide to Available Mathematical
Software (GAMS)} at \url{http://gams.nist.gov}, both as a decision tree and a
text search.

ITK also provides additional numerics functionality. A suite of optimizers, that
use VNL under the hood and integrate with the registration framework
are available. A large collection of statistics functions---not available from
VNL---are also provided in the \code{Insight/Numerics/Statistics}
directory. In addition, a complete finite element (FEM) package is available,
primarily to support the deformable registration in ITK.


\section{Data Representation}
\label{sec:DataRepresentationAndAccess}
%	mesh, image, iterators, various containers

\index{data object} 

There are two principle types of data represented in OTB: images and
meshes. This functionality is implemented in the classes 
Image and Mesh, both of which are subclasses of
\doxygen{itk}{DataObject}. In OTB, data objects are classes that are meant to
be passed around the system and may participate in data flow pipelines (see
Section~\ref{sec:DataProcessingPipeline} on
page~\pageref{sec:DataProcessingPipeline} for more information).


\index{otb::Image}

\doxygen{otb}{Image} represents an \emph{n}-dimensional, regular sampling of
data. The sampling direction is parallel to each of the coordinate axes, and
the origin of the sampling, inter-pixel spacing, and the number of samples in
each direction (i.e., image dimension) can be specified. The sample, or
pixel, type in OTB is arbitrary---a template parameter \code{TPixel}
specifies the type upon template instantiation. (The dimensionality of the
image must also be specified when the image class is instantiated.) The key
is that the pixel type must support certain operations (for example, addition
or difference) if the code is to compile in all cases (for example, to be
processed by a particular filter that uses these operations). In practice the
OTB user will use a C++ simple type (e.g., \code{int}, \code{float}) or a pre-defined pixel
type and will rarely create a new type of pixel class.

One of the important ITK concepts regarding images is that rectangular,
continuous pieces of the image are known as \emph{regions}. Regions are used
to specify which part of an image to process, for example in multithreading,
or which part to hold in memory. In ITK there are three common types of
regions:
\begin{enumerate}
\item \code{LargestPossibleRegion}---the image in its entirety.
\item \code{BufferedRegion}---the portion of the image retained in memory.
\item \code{RequestedRegion}---the portion of the region requested by a 
filter or other class when operating on the image.
\end{enumerate}

The \doxygen{otb}{Image} class extends the functionalities of the
\doxygen{itk}{Image} in order to take into account particular remote
sensing features as geographical projections, etc.

\index{itk::Mesh} 

The Mesh class represents an \emph{n}-dimensional, unstructured grid. The
topology of the mesh is represented by a set of \emph{cells} defined by a 
type and
connectivity list; the connectivity list in turn refers to points.  The
geometry of the mesh is defined by the \emph{n}-dimensional points in
combination with associated cell interpolation functions. \code{Mesh} is
designed as an adaptive representational structure that changes depending on
the operations performed on it. At a minimum, points and cells are required
in order to represent a mesh; but it is possible to add additional topological
information.  For example, links from the points to the cells that use each
point can be added; this provides implicit neighborhood information assuming
the implied topology is the desired one. It is also possible to
specify boundary cells explicitly, to indicate different connectivity
from the implied neighborhood relationships, or to store information
on the boundaries of cells. 

The mesh is defined in terms of three template parameters: 1) a pixel type
associated with the points, cells, and cell boundaries; 2) the dimension of
the points (which in turn limits the maximum dimension of the cells); and 3)
a ``mesh traits'' template parameter that specifies the types of the
containers and identifiers used to access the points, cells, and/or
boundaries. By using the mesh traits carefully, it is possible to create
meshes better suited for editing, or those better suited for ``read-only''
operations, allowing a trade-off between representation flexibility, memory,
and speed.

Mesh is a subclass of \doxygen{itk}{PointSet}. The PointSet
class can be used to represent point clouds or randomly distributed
landmarks, etc. The PointSet class has no associated topology.


\section{Data Processing Pipeline}
\label{sec:DataProcessingPipeline}

\index{data processing pipeline}

\index{process object} 
\index{source}
\index{reader} 
\index{filter} 
\index{mapper} 

While data objects (e.g., images and meshes) are used to represent data,
\emph{process objects} are classes that operate on data objects and may
produce new data objects. Process objects are classed as
\emph{sources}, \emph{filter objects}, or \emph{mappers}.  Sources (such as
readers) produce data, filter objects take in data and process it to produce
new data, and mappers accept data for output either to a file or
some other system.  Sometimes the term \emph{filter} is used broadly
to refer to all three types.

\index{streaming}

The data processing pipeline ties together data objects (e.g., images and
meshes) and process objects. The pipeline supports an automatic updating
mechanism that causes a filter to execute if and only if its input 
or its internal state changes. Further, the data pipeline supports
\emph{streaming}, the ability to automatically break data into smaller
pieces, process the pieces one by one, and reassemble the processed data into
a final result.

Typically data objects and process objects are connected together using the
\code{SetInput()} and \code{GetOutput()} methods as follows:

\small
\begin{verbatim}
  typedef otb::Image<float,2> FloatImage2DType;

  itk::RandomImageSource<FloatImage2DType>::Pointer random;
  random = itk::RandomImageSource<FloatImage2DType>::New();
  random->SetMin(0.0);
  random->SetMax(1.0);

  itk::ShrinkImageFilter<FloatImage2DType,FloatImage2DType>::Pointer shrink;
  shrink = itk::ShrinkImageFilter<FloatImage2DType,FloatImage2DType>::New();
  shrink->SetInput(random->GetOutput());
  shrink->SetShrinkFactors(2);

  otb::ImageFileWriter::Pointer<FloatImage2DType> writer;
  writer = otb::ImageFileWriter::Pointer<FloatImage2DType>::New();
  writer->SetInput (shrink->GetOutput());
  writer->SetFileName( ``test.raw'' );
  writer->Update();
\end{verbatim}
\normalsize 

In this example the source object \doxygen{itk}{RandomImageSource} is connected
to the \doxygen{itk}{ShrinkImageFilter}, and the shrink filter is connected to
the mapper \doxygen{otb}{ImageFileWriter}. When the \code{Update()} method is
invoked on the writer, the data processing pipeline causes each of these
filters in order, culminating in writing the final data to a file on disk.

%\section{Registration Framework}
%\label{sec:RegistrationFramework}
%
%blah blah
%
%\section{FEM Framework}
%\label{sec:FEMFramework}
%
%blah blah
%
\section{Spatial Objects}
\label{sec:SpatialObjectsOverview}
\index{spatial object}
%
The ITK spatial object framework supports the philosophy that the task of
image segmentation and registration is actually the task of object
processing. The image is but one medium for representing objects of interest,
and much processing and data analysis can and should occur at the object
level and not based on the medium used to represent the object.

ITK spatial objects provide a common interface for accessing the physical
location and geometric properties of and the relationship between objects in
a scene that is independent of the form used to represent those objects. That
is, the internal representation maintained by a spatial object may be a list
of points internal to an object, the surface mesh of the object, a continuous
or parametric representation of the object's internal points or surfaces, and
so forth.

The capabilities provided by the spatial objects framework supports their use
in object segmentation, registration, surface/volume rendering, and other
display and analysis functions. The spatial object framework extends the
concept of a ``scene graph'' \index{scene graph} that is common to computer rendering packages so
as to support these new functions. With the spatial objects framework you
can:
\begin{enumerate}

        \item Specify a spatial object's parent and children objects.  In
        this way, a city may contain roads and those roads can be
        organized in a tree structure.

        \item Query if a physical point is inside an object or
        (optionally) any of its children.

        \item Request the value and derivatives, at a physical point,
        of an associated intensity function, as specified
        by an object or (optionally) its children.

        \item Specify the coordinate transformation that maps a parent
        object's coordinate system into a child object's coordinate system.

        \item Compute the bounding box of a spatial object and (optionally)
        its children.

        \item Query the resolution at which the object was originally
        computed.  For example, you can query the resolution (i.e., pixel
        spacing) of the image used to generate a particular instance of a
        \doxygen{itk}{LineSpatialObject}.
\end{enumerate}

Currently implemented types of spatial objects include: Blob, Ellipse,
Group, Image, Line, Surface, and Tube.  The \doxygen{itk}{Scene}
object is used to hold a list of spatial objects that may in turn have
children.  Each spatial object can be assigned a color property.  Each
spatial object type has its own capabilities. For example,
\doxygen{itk}{TubeSpatialObject}s indicate to what point on their parent
tube they connect.

There are a limited number of spatial objects and their methods in ITK, but
their number is growing and their potential is huge. Using the nominal
spatial object capabilities, methods such as mutual
information registration, can be applied to objects regardless of their
internal representation. By having a common API, the same method can be used
to register a parametric representation of a building with an image or
to register two different segmentations of a particular object in
object-based change detection.

%blah blah
%
%\section{Level Set Framework}
%\label{sec:LevelSetFramework}
%
%blah blah
%
%% \section{Wrapping}
%% \label{sec:Wrapping}

%% \index{wrapping}
%% \index{Tcl}
%% \index{Python}

%% While the core of OTB is implemented in C++, Tcl and Python bindings can be
%% automatically generated and OTB programs can be created using these
%% programming languages. This capability is under active development and is for
%% the advanced user only. However, this brief description will give you an idea
%% of what is possible and where to look if you are interested in this facility.

%% The wrapping process in OTB is quite complex due to the use of generic
%% programming (i.e., extensive use of C++ templates). Systems like VTK that use
%% their own wrapping facility are non-templated and customized to the coding
%% methodology found in the system. Even systems like SWIG that are designed
%% for general wrapper generation have difficulty with OTB code because general
%% C++ is difficult to parse. As a result, the OTB wrapper generator uses a
%% combination of tools to produce language bindings.
%% \begin{enumerate}
%%   \item gccxml is a modified version of the GNU compiler gcc that
%%     produces an XML description of an input C++ program.
%%   \item  CABLE processes XML information from gccxml and produces
%%     additional input to the next tool (i.e., CSWIG indicating what is
%%     to be wrapped).
%%   \item CSWIG is a modified version of SWIG that has SWIG's usual
%%     parser replaced with an XML parser (XML produced from CABLE and
%%     gccxml.) CSWIG produces the appropriate language bindings
%%     (either Tcl or Python). (Note: since SWIG is capable of producing
%%     language bindings for eleven different interpreted languages including
%%     Java, and Perl, it is expected that support for some of these languages
%%     will be added in the future.)
%% \end{enumerate}

%% To learn more about the wrapping process, please read the file found in
%% \code{Wrapping/CSwig/README}. Also note that there are some simple test
%% scripts found in \code{Wrapping/CSwig/Tests}. Additional tests and examples
%% are found in the {Testing/Code/*/} directories.

%% The result of the wrapping process is a set of shared libraries/dll's that
%% can be used by the interpreted languages. There is almost a direct
%% translation from C++, with the differences being the particular syntactical
%% requirements of each language. For example, in the directory
%% \code{Testing/Code/Algorithms}, the test
%% \code{itkCurvatureFlowTestTcl2.tcl} has a code fragment that appears as
%% follows: 
%% \small
%% \begin{verbatim}
%%   set reader [itkImageFileReaderF2_New]
%%     $reader SetFileName "${OTB_TEST_INPUT}/cthead1.png"

%%   set cf [itkCurvatureFlowImageFilterF2F2_New]
%%     $cf SetInput [$reader GetOutput]
%%     $cf SetTimeStep 0.25
%%     $cf SetNumberOfIterations 10
%% \end{verbatim}
%% \normalsize
%% The same code in C++ would appear as follows:

%% \small
%% \begin{verbatim}
%%   otb::ImageFileReader<ImageType>::Pointer reader = 
%%               otb::ImageFileReader<ImageType>::New();
%%   reader->SetFileName("cthead1.png");

%%   itk::CurvatureFlowImageFilter<ImageType,ImageType>::Pointer cf =
%%       itk::CurvatureFlowImageFilter<ImageType,ImageType>::New();
%%     cf->SetInput(reader->GetOutput());
%%     cf->SetTimeStep(0.25);
%%     cf->SetNumberOfIterations(10);
%% \end{verbatim}
%% \normalsize

%% This example demonstrates an important difference between C++ and a wrapped
%% language such as Tcl.  Templated classes must be instantiated prior to
%% wrapping. That is, the template parameters must be specified as part of the
%% wrapping process. In the example above, the
%% \code{CurvatureFlowImageFilterF2F2} indicates that this filter has been
%% instantiated using an input and output image type of two-dimensional float
%% values (e.g., \code{F2}). Typically just a few common types are selected for
%% the wrapping process to avoid an explosion of types and hence, library
%% size. To add a new type requires rerunning the wrapping process to produce
%% new libraries.

%% The advantage of interpreted languages is that they do not require the
%% lengthy compile/link cycle of a compiled language like C++. Moreover, they
%% typically come with a suite of packages that provide useful
%% functionality. For example, the Tk package (i.e., Tcl/Tk and Python/Tk)
%% provides tools for creating sophisticated user interfaces. In the future it
%% is likely that more applications and tests will be implemented in the various
%% interpreted languages supported by OTB.


%
%blah blah
%
%\section{Auxiliary \& Utilities}
%\label{sec:Auxiliary}
%\label{sec:Utilities}
%
%calculators and classes supporting the data processing pipeline;
%utilities such as GUI interface tools
