\chapter{Image Visualization and output}
\label{chap:ImageVisualization}

After processing your images with OTB, you probably want to see the result. As it is quite straightforward in some situation, if can be a bit trickier in other. For example, some filters will give you a list of polygons as an output. Other can return an image with each region labelled by a unique index. In this section we are going to provide few examples to help you produce beautiful output ready to be included in your publications/presentations.


\section{Viewer}
Even if OTB is not a visualization toolkit as for instance VTK
(\emph{The Visualization Toolkit} \url{http://www.vtk.org}), some
simple functionalities for image visualization are given in the
toolbox. Indeed, for algorithm prototyping, it is sometimes more
useful to \emph{see} the result on the screen, than saving it to a
file and then open in with an external viewer.

OTB provides the \doxygen{otb}{ImageViewer} class which is compatible
with the pipeline and can therefore replace the
\doxygen{otb::ImageFileWriter} during proto-typing phases.

\input{VisuExample1.tex}


\section{Images}

\subsection{Grey Level Images}
\label{sec:ViewingGreyLevelImages}

\input{ScalingFilterExample.tex}

\subsection{Multiband Images}
\label{sec:ViewingMultibandImages}

\input{PrintableImageFilterExample.tex}

\subsection{Indexed Images}
\label{sec:ViewingIndexedImages}

\input{IndexedToRGBExample.tex}

\subsection{Altitude Images}
\label{sec:ViewingAltitudeImages}

\input{DEMToRainbowExample.tex}
